validateE2data

### 2018-08-29 E2/analysis/doEverything.Rmd
this is going well

---
title: "inspect histograms"
author: "Alex Holcombe"
date: "2/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r validate data, echo=FALSE, message=FALSE}
source('validateE2data.Rmd')
```

@@

```{r load data, echo=FALSE, message=FALSE}
source('importE2data.Rmd')
```

inspect Hists for weird data, non-performing Ss

```{r inspectHists}

source('inspectHists.Rmd')
```

@@

```{r}
source('mixModelE2data.Rmd')
```

Plot hists with psychophysical curves added,
check that and likelihood ratio test for whether to exclude, 
and infer
```{r}
source('inspectHistsWithFits.Rmd')
```

>>>>

---
title: "Do everything"
author: "Alex Holcombe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

The idea of this document is to have a single file that when knit does everything, [calling subsidiary Rmd documents](https://stackoverflow.com/questions/41962434/source-code-from-rmd-file-within-another-rmd)

But the problem is, the importE2data.Rmd throws a bizarre error when knit, but not when run!
Moreover, importE2data takes a very long time to run.
So in practice, the better thing to do is to run the below files one by one.

@@

```{r validate, child = 'validateE2data.Rmd'}
```

@@

```{r import, child = 'importE2data.Rmd'}
```

Inspect Hists for weird data, non-performing Ss.  This is prior to mixture modeling. Will do again after mixture modeling.

```{r inspectHists, child = 'inspectHists.Rmd'}
```

@@

```{r inspectHists, child = 'mixModelE2data.Rmd'}
```

Plot two-target hists with psychophysical curves added,
check that and likelihood ratio test for whether to exclude, 
```{r, child= 'histsWithFitsTwoTarget.Rmd'}
```

Plot one-target hists with psychophysical curves added,

```{r, child= 'histsWithFitsOneTarget.Rmd'}
```

Do exclusions, add column indicating whether subject excluded to dataframe, save that.
Should also add handedness quotient from handednessQuotientsP2E2 but there are so few left-handers it wouldn't make a difference. Need to pool across papers to test handedness issue.
```{r, child ='exclusions.Rmd')}
```

Look at incidence of location swaps.

What will I do about orientation? I can see how often they get orientation wrong, but that by itself is not so interesting.
I can look at the serial position correlogram of orientation and letter identity and I expect to see quite a strong correlation, contrary to what was found for two letters but something it would make sense to report at same time as Cheryl's finding.

### 2018-08-29 E2/analysis/exclusions.Rmd
this is going well

---
title: "one target"
author: "Alex Holcombe"
date: "2/26/2018"
output: html_document
---

@@

Set up the experiment-specific parameters

```{r detailsNeeded}

numItemsInStream<- length( dg$letterSeq[[1]] )  
minSPE<- -17; maxSPE<- 17
annotateIt<-TRUE

numSs<-length(unique(dg$subject))
cat( paste0('Total num Ss=',numSs) )
```

Calc numObservations for each condition
```{r }
#Calc numObservations for each condition. This is needed  for scaling the fine-grained Gaussian
#gaussianScaledforData needs to know.
if (!("nPerCond" %in% colnames(dg))) {
  dfGroups<-  dg  %>%  filter( !is.na(targetSP) ) %>% group_by_at(.vars = condtnVariableNames) %>% summarise(nPerCond = n())
  #add nPerCond back to parameter estimates
  estimates<- merge(estimates,dfGroups)
}
```

Calculate curves for parameters, to plot on histograms.
```{r, echo=TRUE, message=FALSE, fig.height=360, fig.width=10}
#devtools::install_github('alexholcombe/mixRSVP',build_vignettes=TRUE)
library(mixRSVP)
oneTarget<- dg %>% filter(targetSide!="Both")
curvesOneTarget<- dg %>% filter(targetSide!="Both") %>%
  group_by_at(.vars = condtnVariableNames) %>% 
  do(calc_curves_dataframe(.,minSPE,maxSPE,numItemsInStream))
#fails with on-missing arguments to min; returning Inf no non-missing arguments to max; returning -Inf 
#Error in createGuessingDistribution(minSPE, maxSPE, df$targetSP, numItemsInStream) :  minSPE must be less than or equal to maxSPE

#DEBUG
# dd<- dg %>% filter(subject=="AA", stream=="Left",targetSide=="Both",orientation=="Canonical")
# 
# createGuessingDistribution(minSPE,maxSPE,dd$targetSP,numItemsInStream)
# targetSP<- dd$targetSP
# maxTargetSP <- max(targetSP)
# minSPEthisData<- 1 - max(targetSP)
# maxSPEthisData<- numItemsInStream - min(targetSP)
# if (maxSPEthisData > maxSPE) stop("maxSPE must be at least",maxSPEthisData,"based on the values you passed me")
# if (minSPEthisData < minSPE) stop("minSPE must be no greater than",minSPEthisData,"based on the values you passed me")
# calc_curves_dataframe(dd,minSPE,maxSPE,numItemsInStream)

```{r }
# #Calc numObservations to each condition. This is needed only for scaling the fine-grained Gaussian
# #Calc the number of observations for each condition, because gaussianScaledforData needs to know.
# dfGroups<- dg %>% group_by_at(.vars = condtnVariableNames) %>% summarise(nPerCond = n())
# #add nPerCond back to parameter estimates
# estimates<- merge(estimates,dfGroups)

grain<-.05
gaussFine<- estimates %>%  filter(targetSide!="Both") %>% group_by_at(.vars = condtnVariableNames) %>% do(
  gaussian_scaled_from_df(.,minSPE,maxSPE,grain) )
```

Plot sample histograms, make sure plotting working.

```{r singleHistPlot}
library(ggplot2)

dAC<- dplyr::filter(oneTarget,subject=="AC")  
plotContinuousGaussian<- TRUE 
annotateIt<-TRUE
g<- plot_hist_with_fit(dAC,minSPE,maxSPE,d915$targetSP,numItemsInStream,
                        plotContinuousGaussian,annotateIt, FALSE)
g <- g + geom_vline(xintercept = 0)
g + annotate("text", x = 12, y = 25, label = "AC")
```

Show single plot with curves using scalable method to facet_grid.
In other words, make sure can plot without plot_hist_with_fit

```{r singleHistPlotScalable, echo=FALSE}

dAC<- dplyr::filter(oneTarget,subject=="AC")  
curvesThis <- curvesOneTarget %>% filter(subject=="AC")

g=ggplot(dAC, aes(x=SPE)) + 
        facet_grid(orientation~stream) #,  scales="free_y")
g<-g+geom_histogram(binwidth=1,color="grey90") + xlim(minSPE,maxSPE)
g<-g+ geom_text(x=12, y= 33, aes(label = subject)) #inset subject name/number. Unfortunately it overwrites itself a million times
g<-g +theme_apa() #+theme(panel.grid.minor=element_blank(),panel.grid.major=element_blank())# hide all gridlines.
g<-g +xlim(minSPE,maxSPE)
sz=.3
#show(g)
g<-g+ geom_point(data=curvesThis,aes(x=x,y=combinedFitFreq),color="chartreuse3",size=sz)

#g<-g+ geom_line(data=curves,aes(x=x,y=guessingFreq),color="yellow",size=sz)
#Discretized Gaussian
#g<-g+ geom_line(data=curves,aes(x=x,y=gaussianFreq),color="lightblue",size=sz)

#mixSig - whether mixture model statistically significantly better than guessing
curvesThis <- dplyr::mutate(curvesThis, mixSig = ifelse(pLRtest <= .05, TRUE, FALSE)) #annotate_fit uses this to color the p-value
g<- annotate_fit(g,curvesThis) #assumes curvesDf includes efficacy,latency,precision
#Somehow the which mixSig (TRUE or FALSE) is red and which green is flipped relative to plot_hist_with_fit even though
#identical commands are used. I haven't been able to work out why.
#g<- g + scale_color_manual(values=c("red","forestgreen")) #already done in annotate_fit
show(g)
```

Plot all Ss
```{r, fig.height=200, fig.width=10}

g=ggplot(oneTarget, aes(x=SPE)) + 
        facet_grid(subject+orientation~stream) #,  scales="free_y")
g<-g+geom_histogram(binwidth=1,color="grey90") + xlim(minSPE,maxSPE)
g<-g+ geom_text(x=12, y= 33, aes(label = subject)) #inset subject name/number. Unfortunately it overwrites itself a million times
g<-g +theme_apa() #+theme(panel.grid.minor=element_blank(),panel.grid.major=element_blank())# hide all gridlines.
g<-g +xlim(minSPE,maxSPE)
sz=.3
#show(g)
g<-g+ geom_point(data=curvesOneTarget,aes(x=x,y=combinedFitFreq),color="chartreuse3",size=sz)
#g<-g+ geom_line(data=curves,aes(x=x,y=guessingFreq),color="yellow",size=sz)
#Discretized Gaussian
#g<-g+ geom_line(data=curves,aes(x=x,y=gaussianFreq),color="lightblue",size=sz)

#mixSig - whether mixture model statistically significantly better than guessing
curvesOneTarget <- dplyr::mutate(curvesOneTarget, mixSig = ifelse(pLRtest <= .05, TRUE, FALSE)) #annotate_fit uses this to color the p-value
g<- annotate_fit(g,curvesOneTarget) #assumes curvesDf includes efficacy,latency,precision
#Somehow the which mixSig (TRUE or FALSE) is red and which green is flipped relative to plot_hist_with_fit even though
#identical commands are used. I haven't been able to work out why.
#g<- g + scale_color_manual(values=c("red","forestgreen")) #already done in annotate_fit
show(g)

@@

## Exclusions

@@

#for each subject, count pLRtest instances >.05 and efficay <.1
B<-tw %>% ungroup %>% group_by(subject) %>% summarise(LRtestFails = sum(pLRtest>.05), effFails = sum(efficacy<.1))                                                              
#B %>% print(n=Inf)
LRtestLosers <- B %>% filter(LRtestFails>=3)
LRtestLosers<- unique(LRtestLosers$subject)
# efficacy is below 10% in both streams in either the upright or the reversed orientation.
# To calculate that, need to group by subject and orientation
C<-tw %>% ungroup %>% group_by(subject,orientation) %>% summarise(bothEffsFailed = sum(efficacy<.1)==2)
#Find which subjects, if any, has a bothEffsFailed==TRUE
lowEff<- C %>% filter(bothEffsFailed==TRUE)
lowEffs <- unique(lowEff$subject)
```

@@

Will also exclude if difference in efficacy left-right exceeds?
```{r }
#Calculate exclusions based on one-target performance
#oneTarget<- dg %>% filter(targetSide!="Both")
one<- oneTarget %>% group_by(subject,targetSide,orientation) %>% 
  select(-targetStreamOrientations,-letterSeq) %>% #can't include list columns
  select(-trial,-targetSP,-respSP,-respOrder) %>% #clear detritus so easier to see
  summarise_all( function(x){ if(is.numeric(x)){ return(mean(x)) } else{ nth(x,-1) } })

#Look at the difference in efficacy between the left and the right
effDiff <- function(df) {
  #dgi<<-df
  #STOP
  effLeft<- (df %>% filter(targetSide=="Left"))$efficacy 
  effRight<- (df %>% filter(targetSide=="Right"))$efficacy
  df$effDiff<- effLeft - effRight
  df$efficacy<- mean(c(effLeft,effRight))
  df$effDiff<- effLeft - effRight

@@

oneDiff<- one %>% group_by(subject,orientation) %>% do( effDiff(.) )
oneDiff<- oneDiff %>% select(subject,targetSide,orientation,efficacy,effDiff,pLRtest,failedBothLR)
oneDiff

oneTargetLosers <- oneDiff %>% filter(failedBothLR == TRUE, effDiff > .4)

@@

```{r}
#To do that, do I need to unmelt?
ggplot(one, aes(x=
```

@@

Make master list of Ss to exclude also from one-target condition??

Actually exclude the losers
```{r exclude, echo=FALSE}

afterExclusions<- tw %>% filter(  !(subject %in% lowEffs)   )

A<- tw %>% filter(subject=="AA")
B<-A %>% ungroup %>% summarise(LRtestFails = sum(pLRtest<.05), effFails = sum(efficacy<.1))

twoTarget %>% select(-targetStreamOrientations,-warnings,-letterSeq) %>% group_by(stream,orientation) %>% summarise_all(funs(if_else(is.numeric(.), mean(.), 3))

two<- twoTarget %>% group_by(stream,orientation) %>% summarise_all(funs(if_else(!is.list(.), mean(.), last(.))))

  summarise_all(funs(mean,sd))
A <- two %>% filter(subject=="AA")

curvesOneTarget<- twoTarget %>%
  group_by(subject) %>% 
  do(calc_curves_dataframe(.,minSPE,maxSPE,numItemsInStream))

Participant AI, BB suspicion of  attending to one side from twoTargets condition.

>>>>

---
title: "Exclusions"
author: "Alex Holcombe"
date: "2/26/2018"
output: html_document
---

@@

One-target:

@@

BG, BJ, and AP have sigma near 4, clear outliers.

## Exclusions based on two-target conditions

Notes from histsWithFitsTwoTarget.Rmd:
AP, especially BJ does flunk likelihood test! CY passes but data not horrifyingly bad.
Exclude by likelihood-ratio test.
Participant AI, BB suspicion of  attending to one side from twoTargets condition.

@@

#for each subject, count pLRtest instances >.05 and efficay <.1
B<-tw %>% ungroup %>% group_by(subject) %>% summarise(LRtestFails = sum(pLRtest>.05), effFails = sum(efficacy<.1))                                                              
#B %>% print(n=Inf)
LRtestLosers <- B %>% filter(LRtestFails>=3)
LRtestLosers<- unique(LRtestLosers$subject)
# efficacy is below 10% in both streams in either the upright or the reversed orientation.
# To calculate that, need to group by subject and orientation
C<-tw %>% ungroup %>% group_by(subject,orientation) %>% summarise(bothEffsFailed = sum(efficacy<.1)==2)
#Find which subjects, if any, has a bothEffsFailed==TRUE
lowEff<- C %>% filter(bothEffsFailed==TRUE)
lowEffLosers <- unique(lowEff$subject)
```

## Exclusions based on one-target conditions

@@

Will also exclude if difference in efficacy left-right exceeds?
```{r }
#Calculate exclusions based on one-target performance
oneTarget<- dg %>% filter(targetSide!="Both")
one<- oneTarget %>% group_by(subject,targetSide,orientation) %>% 
  select(-targetStreamOrientations,-letterSeq) %>% #can't include list columns
  select(-trial,-targetSP,-respSP,-respOrder) %>% #clear detritus so easier to see
  summarise_all( function(x){ if(is.numeric(x)){ return(mean(x)) } else{ nth(x,-1) } })

#Look at the difference in efficacy between the left and the right
effDiff <- function(df) {
  #dgi<<-df
  #STOP
  effLeft<- (df %>% filter(targetSide=="Left"))$efficacy 
  effRight<- (df %>% filter(targetSide=="Right"))$efficacy
  df$effDiff<- effLeft - effRight
  df$effLeft <- effLeft; df$effRight <- effRight

  df$efficacy<- mean(c(effLeft,effRight))
  df$effDiff<- effLeft - effRight

@@

oneDiff<- one %>% group_by(subject,orientation) %>% do( effDiff(.) )
oneDiff %>% select(subject,targetSide,orientation,efficacy,effDiff,pLRtest,failedBothLR)

oneTargetLosers <- oneDiff %>% filter(failedBothLR == TRUE, effDiff > .4)
oneTargetLosers<- unique(oneTargetLosers$subject)
```

```{r}
#To do that, do I'd either need to unmelt (spread) but rather than do that, I programmed putting effLeft and effRight on same row into effDiff
g<- ggplot(oneDiff, aes(x=effLeft, y=effRight, color=orientation)) + geom_point()
g<-g +  geom_abline(intercept = 0, slope = 1) + theme_apa() + xlim(0,1) + ylim(0,1)
g +    geom_rug(col=rgb(.5,0,0,alpha=.2))

@@

@@

I now have LRtestLosers, lowEffLosers, and oneTargetLosers

Actually exclude the losers? Probably better if flag them so can run inferential stats both with and without them.

```{r exclude, echo=FALSE}
allLosers <- unique( c(LRtestLosers, lowEffLosers, oneTargetLosers) )
#afterExclusions<- dat %>% filter(  !(subject %in% lowEffs)   )
dat <- dat %>% mutate(exclude = (subject %in% allLosers))
#table(dat$subject,dat$exclude)
```

Next stop, inferential stats?  Save data with estimates and exclude field added.

```{r exclude, echo=FALSE}

pathToSave <- file.path( "..","Data")
saveRDS(dat, file.path(pathToSave,"backwards2E2_dataWithEstimatesAndExcludeColumn.rda"), compress = "bzip2")
```

### 2018-08-29 E2/analysis/histsWithFitsOneTarget.Rmd
this is going well

---
title: "one target"
author: "Alex Holcombe"
date: "2/26/2018"
output: html_document
---

@@

## Exclusions

Exclude by likelihood ratio test and efficacy.

For each subject, calculate how many two-target streams they failed. If 3 or 4 of 4, exclude (didn't think to mention 1-target condition in prereg).

Also check whether average efficacy is below 10% in both streams in either the upright or the reversed orientation.

```{r exclusions}

twoTarget<- dg %>% filter(targetSide=="Both")

AA<- twoTarget %>% filter(subject=="AA")
#Function for one subject, calculating how many stream conditions failed the test
calcExclude<- function(oneSub) {
  oneSub %>% group_by(stream,orientation)
}
#first, collapse over trials
#https://stackoverflow.com/questions/51978519/summarise-numeric-columns-return-last-value-of-non-numeric
tw<- twoTarget %>% group_by(subject,stream,orientation) %>% select(-targetStreamOrientations,-letterSeq) %>% #can't include list columns
  summarise_all( function(x){ if(is.numeric(x)){ return(mean(x)) } else{ nth(x,-1) } })

#for each subject, count pLRtest instances >.05 and efficay <.1
B<-tw %>% ungroup %>% group_by(subject) %>% summarise(LRtestFails = sum(pLRtest>.05), effFails = sum(efficacy<.1))                                                              
#B %>% print(n=Inf)
exclude <- B %>% filter(LRtestFails>=3, effFails >

# efficacy is below 10% in both streams in either the upright or the reversed orientation.
# To calculate that, need to group by subject and orientation
C<-tw %>% ungroup %>% group_by(subject,orientation) %>% summarise(bothEffsFailed = sum(efficacy<.1)==2)
#Find which subjects, if any, has a bothEffsFailed==TRUE
lowEff<- C %>% filter(bothEffsFailed==TRUE)
lowEff <- unique(lowEff$subject)

A<- tw %>% filter(subject=="AA")
B<-A %>% ungroup %>% summarise(LRtestFails = sum(pLRtest<.05), effFails = sum(efficacy<.1))

twoTarget %>% select(-targetStreamOrientations,-warnings,-letterSeq) %>% group_by(stream,orientation) %>% summarise_all(funs(if_else(is.numeric(.), mean(.), 3))

two<- twoTarget %>% group_by(stream,orientation) %>% summarise_all(funs(if_else(!is.list(.), mean(.), last(.))))

  summarise_all(funs(mean,sd))
A <- two %>% filter(subject=="AA")

curvesOneTarget<- twoTarget %>%
  group_by(subject) %>% 
  do(calc_curves_dataframe(.,minSPE,maxSPE,numItemsInStream))

>>>>

---
title: "one target"
author: "Alex Holcombe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

### 2018-08-29 E2/analysis/importE2data.Rmd
this is going well

E<- readInAllFiles(rawDataPath)
#TT<- as_tibble(E).  Seems to have no effect because weird hybrid type

#Calculate the serial position error
E$SPE<- E$respSP - E$targetSP

#give targetSide values that make  sense, like "dual", "left", and "right"
E<- E %>% mutate(targetSide = case_when(targetSide==0 ~ "both", 
                                       targetSide==1 ~"left", targetSide==2 ~"right",
                                       TRUE ~ "unexpected value"))
```

@@

```{r veryTimeConsuming}
#Need to decompose into SPE=-3 orientation, SPE=-2 orientation, etc.
#Hm, can I use list apply to go through every row and pull out relevant bits?
#Very time-consuming!
E$orientMinus3<- -99; E$orientMinus2<- -99; E$orientMinus1<- -99; E$orient0<- -99; E$orientPlus1<- -99; E$orientPlus2<- -99;

for (i in 1:nrow(E)) {
  #row<- E[i,]
  #orientsThis <- row$targetStreamOrientations[[1]]
  #targetPos <- row$targetSP
  #If targetSP == NaN, it's a one-target trial and wrong side
  if (is.nan(E[i,]$targetSP)) {
    E[i,]$orientMinus3 <- NaN
  } else {
    E[i,]$orientMinus4 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP -4    ]
    E[i,]$orientMinus3 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP -3    ]
    E[i,]$orientMinus2 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP -2    ]
    E[i,]$orientMinus1 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP -1    ]
    E[i,]$orient0 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP    ]
    E[i,]$orientPlus1 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP +1    ]
    E[i,]$orientPlus2 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP +2    ]
  }
}

# More explicit way of doing it below but might take more time.
# for (i in 1:nrow(E)) {
#   row<- E[i,]
#   orientsThis <- row$targetStreamOrientations[[1]]
#   targetPos <- row$targetSP
#   #If targetSP == NaN, it's a one-target trial and wrong side
#   if (is.nan(targetPos)) {
#     E[i,]$orientMinus3<- NaN
#   }
#   E[i,]$orientMinus3<- orientsThis[targetPos-3]
#   #E[i,]$orientMinus3<- E[i,]$targetStreamOrientations[[1]][targetPos-3]
#   E[i,]$orientMinus2<- orientsThis[targetPos-2]
#   E[i,]$orientMinus1<- orientsThis[targetPos-1]
#   E[i,]$orient0<- orientsThis[targetPos] #should be same as $targetOrient
#   E[i,]$orientPlus1<- orientsThis[targetPos+1]
#   E[i,]$orientPlus2<- orientsThis[targetPos+2]
# }
```

Saving data.
```{r saveData}
backwards2_E2 <- E
pathToSave <- file.path( "..","Data")
saveRDS(backwards2_E2, file = "../Data/backwards2E1_rawDataFromMAT.rda", compress="bzip2")
```

>>>>

Ee<- readInAllFiles(rawDataPath)
#TT<- as_tibble(E).  Seems to have no effect because weird hybrid type

#Calculate the serial position error
Ee$SPE<- Ee$respSP - Ee$targetSP

#give targetSide values that make  sense, like "dual", "left", and "right"
Ee<- Ee %>% mutate(targetSide = case_when(targetSide==0 ~ "both", 
                                       targetSide==1 ~"left", targetSide==2 ~"right",
                                       TRUE ~ "unexpected value"))
```

@@

```{r veryTimeConsuming}
#Need to decompose into SPE=-3 orientation, SPE=-2 orientation, etc.
#Hm, can I use list apply to go through every row and pull out relevant bits?
#Very time-consuming!
Ee$orientMinus3<- -99; Ee$orientMinus2<- -99; Ee$orientMinus1<- -99; Ee$orient0<- -99; Ee$orientPlus1<- -99; Ee$orientPlus2<- -99;

for (i in 1:nrow(Ee)) {
  #row<- E[i,]
  #orientsThis <- row$targetStreamOrientations[[1]]
  #targetPos <- row$targetSP
  #If targetSP == NaN, it's a one-target trial and wrong side
  if (is.nan(Ee[i,]$targetSP)) {
    Ee[i,]$orientMinus3 <- NaN
  } else {
    Ee[i,]$orientMinus4 <- Ee[i,]$targetStreamOrientations[[1]][    Ee[i,]$targetSP -4    ]
    Ee[i,]$orientMinus3 <- Ee[i,]$targetStreamOrientations[[1]][    Ee[i,]$targetSP -3    ]
    Ee[i,]$orientMinus2 <- Ee[i,]$targetStreamOrientations[[1]][    Ee[i,]$targetSP -2    ]
    Ee[i,]$orientMinus1 <- Ee[i,]$targetStreamOrientations[[1]][    Ee[i,]$targetSP -1    ]
    Ee[i,]$orient0 <- Ee[i,]$targetStreamOrientations[[1]][    Ee[i,]$targetSP    ]
    Ee[i,]$orientPlus1 <- Ee[i,]$targetStreamOrientations[[1]][    Ee[i,]$targetSP +1    ]
    Ee[i,]$orientPlus2 <- Ee[i,]$targetStreamOrientations[[1]][    Ee[i,]$targetSP +2    ]
  }
}

# More explicit way of doing it below but might take more time.
# for (i in 1:nrow(E)) {
#   row<- Ee[i,]
#   orientsThis <- row$targetStreamOrientations[[1]]
#   targetPos <- row$targetSP
#   #If targetSP == NaN, it's a one-target trial and wrong side
#   if (is.nan(targetPos)) {
#     Ee[i,]$orientMinus3<- NaN
#   }
#   Ee[i,]$orientMinus3<- orientsThis[targetPos-3]
#   #Ee[i,]$orientMinus3<- Ee[i,]$targetStreamOrientations[[1]][targetPos-3]
#   Ee[i,]$orientMinus2<- orientsThis[targetPos-2]
#   Ee[i,]$orientMinus1<- orientsThis[targetPos-1]
#   Ee[i,]$orient0<- orientsThis[targetPos] #should be same as $targetOrient
#   Ee[i,]$orientPlus1<- orientsThis[targetPos+1]
#   Ee[i,]$orientPlus2<- orientsThis[targetPos+2]
# }
```

Rename some columns
```{r renameColumns}
#Something bizarre happens when knitting this, the below command throws error. But no problem when running without knitting
#Error in names(E)[names(E) == "target"] <- "stream" :   names() applied to a non-vector
names(Ee)[names(Ee) == 'target'] <-'stream'
names(Ee)[names(Ee) == 'condition'] <-'orientation'
Ee$stream[ Ee$stream==1 ] <- "Left"
Ee$stream[ Ee$stream==2 ] <- "Right"
Ee$targetSide[ Ee$targetSide==0 ] <- "Both"
Ee$targetSide[ Ee$targetSide==1 ] <- "Left"
Ee$targetSide[ Ee$targetSide==2 ] <- "Right"

#Give orientations some better names.
Ee$orientation[ Ee$orientation==1 ] <- "Canonical"
Ee$orientation[ Ee$orientation==2 ] <- "Inverted"
```

Saving data.
```{r saveData}
backwards2_E2 <- Ee
pathToSave <- file.path( "..","Data")
saveRDS(backwards2_E2, file = "../Data/backwards2E2_rawDataFromMAT.rda", compress="bzip2")
```

### 2018-08-29 E2/analysis/validateE2data.Rmd
this is going well

---
title: "importE2data"
author: "Alex Holcombe"
date: "2/27/2018"
output: html_document
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

>>>>

---
title: "validateE2data"
author: "Alex Holcombe"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

Optional validation (don't have to run this to go to next step), loads raw data on its own and validates a few things

@@

@@

Sanity-check some data by graphing.

Investigate whether pathological identicalness of inverted/canonical happens, that happened in E1 . Seems it doesn't

```{r}
dg<- E2 %>% filter(subject < "AC")

library(ggplot2)
g=ggplot(dg, aes(x=SPE)) + facet_grid(subject+orientation~stream) #,  scales="free_y")
minSPE<- -17; maxSPE<- 17  #But it's 16 items in stream, so shouldn't it be -15, +15?
g<-g+geom_histogram(binwidth=1,color="grey90") + xlim(minSPE,maxSPE)
g<-g+ geom_text(x=12, y= 33, aes(label = subject)) #inset subject name/number. Unfortunately it overwrites itself a million times
show(g)
```
